AggregateCounts

### 2021-09-07 R/AggregateCounts.Rmd
added plots with factes for species. Finalized first version of figures for chapter

PlotBiomasPerSampleAndCondition<-function(df1,df2, df3, species){
ggplot()+ 
    geom_point(data = df1 %>% filter(TimePoint=="Day 4") %>% filter(Species==species), aes(x = SaStrain, y= meanBiomassLog,shape = Region), 
             position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75), size = 4)+
  geom_point(data = df2%>% filter(TimePoint=="Day 4") %>% filter(Species==species), aes(x = SaStrain, y= log10(biomass), shape = Region),size = 1, 
             position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75))+ 
  geom_point(data = df3 %>% filter(TimePoint=="Day 4") %>% filter(Species==species), aes(x = SaStrain, y= meanBiomassLog), shape = 3, size = 4)+
    #scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)), limits = c(1, 100000000))+
      facet_grid(.~Species, scales = "free", space = "free") +
  ggtitle('Total Biomass')+
  labs(x = "",y = bquote(paste("Volume (log10", mu*"m"^3*")")))+
  scale_color_brewer(palette = "Set1")+
  scale_shape_manual(values=c(16, 1))+
  ylim(0,8)+
    theme_cowplot()+
  panel_border() +
  theme(plot.title = element_text(hjust = 0.5), 
        strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
}
PlotBiomasPerSampleAndCondition(aggregateListSummaryCondition,
                                aggregateListSummaryReplicate,
                                aggregateListSummaryCondNoRegion, "S. aureus")

PlotMeanAggsPerSampleAndConditionWT<-function(df1,df2, df3){
ggplot()+ 
    geom_point(data = df1 %>% filter(TimePoint=="Day 4"), aes(x = Culture, y= meanAggs,shape = Region), 
             position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75), size = 4)+
  geom_point(data = df2%>% filter(TimePoint=="Day 4"), aes(x = Culture, y= Aggs, shape = Region),size = 1, 
             position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75))+
    geom_point(data = df3 %>% filter(TimePoint=="Day 4"), aes(x = Culture, y= meanAggs),shape = 3,size = 4)+
    scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)), limits = c(10, 100000))+
      facet_grid(.~Species, scales = "free", space = "free") +
  ggtitle('Number of groups of bacteria')+
  labs(x = "",y = "")+
  scale_color_brewer(palette = "Set1")+
  scale_shape_manual(values=c(16, 1))+
  #ylim(0,8)+
    theme_cowplot()+
  panel_border() +
  theme(plot.title = element_text(hjust = 0.5), 
        strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
}
PlotMeanAggsPerSampleAndConditionWT(aggregateListSummaryCondition%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "Pa wt mono"),
                                aggregateListSummaryReplicate %>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "Pa wt mono"), 
                                aggregateListSummaryCondNoRegion%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "Pa wt mono"))

PlotMeanAggsPerSampleAndCondition<-function(df1,df2, df3,species){
ggplot()+ 
    geom_point(data = df1 %>% filter(TimePoint=="Day 4") %>% filter(Species == species), aes(x = SaStrain, y= meanAggs,shape = Region), 
             position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75), size = 4)+
  geom_point(data = df2%>% filter(TimePoint=="Day 4")%>% filter(Species == species), aes(x = SaStrain, y= Aggs, shape = Region),size = 1, 
             position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75))+
    geom_point(data = df3 %>% filter(TimePoint=="Day 4")%>% filter(Species == species), aes(x = SaStrain, y= meanAggs),shape = 3,size = 4)+
    scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)), limits = c(10, 100000))+
      #facet_grid(, scales = "free", space = "free") +
  ggtitle('Number of groups of bacteria')+
  labs(x = "",y = "")+
  scale_color_brewer(palette = "Set1")+
  scale_shape_manual(values=c(16, 1))+
  #ylim(0,8)+
    theme_cowplot()+
  panel_border() +
  theme(plot.title = element_text(hjust = 0.5), 
        strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
}
PlotMeanAggsPerSampleAndCondition(aggregateListSummaryCondition,
                                aggregateListSummaryReplicate, 
                                aggregateListSummaryCondNoRegion, "S. aureus")

@@

```
```{r figures 1A,1B and 2A, 2B}
#Biomass wt
PlotBiomasPerSampleAndConditionWT(aggregateListSummaryCondition%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "Pa wt mono"),
                                aggregateListSummaryReplicate %>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "Pa wt mono"), 
                                aggregateListSummaryCondNoRegion%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "Pa wt mono"))
#Biomass Sa and mutants
PlotBiomasPerSampleAndCondition(aggregateListSummaryCondition,
                                aggregateListSummaryReplicate,
                                aggregateListSummaryCondNoRegion, "S. aureus")

PlotBiomasPerSampleAndCondition(aggregateListSummaryCondition,
                                aggregateListSummaryReplicate,
                                aggregateListSummaryCondNoRegion, "P. aeruginosa")

@@

#Number of aggregates Sa and mutants
PlotMeanAggsPerSampleAndCondition(aggregateListSummaryCondition,
                                aggregateListSummaryReplicate, 
                                aggregateListSummaryCondNoRegion, "S. aureus")

PlotMeanAggsPerSampleAndConditionPa(aggregateListSummaryCondition,
                                aggregateListSummaryReplicate, 
                                aggregateListSummaryCondNoRegion, "P. aeruginosa")
```

@@

#this pipe essentially gets to the product of what fancy histograms do but more efficiently
#First including all sizes
#####

@@

#Summary data frame
HistConditionSummary<-HistCondition %>%
  group_by(Species,SaStrain,Strain,Culture,TimePoint,Condition,LogBin,NormalizedFrequency,NormalizedBiomass) %>% 
  summarize() %>% unique()%>%ungroup() %>%
  group_by(Species,SaStrain,Strain,Culture,TimePoint,Condition) %>% 
  mutate(checkSumFreq =sum(NormalizedFrequency), checkSumBiomass = sum(NormalizedBiomass))
#####

#Now per condition including region. The difference is int the "group_by" part
#####
HistConditionRegin<-aggregateList %>% mutate(LogBin = case_when(Size <= 5 ~ "(.5, 5]",
                        Size<= 10 ~ "(5, 10]",
                        Size<= 100    ~ "(10, 100]",
                        Size<= 1000   ~ "(100, 1000]",
                        Size> 1000  ~ paste0("(1000, ",bquote("\U221E"), ")"))) %>% 
  group_by(Species,Condition,TimePoint,Region)%>% 
  mutate(TotalBiomass = sum(Size), TotalFrequency = n()) %>% ungroup() %>%
  group_by(Species,Condition,TimePoint,Region,LogBin)%>%
  mutate(BinBiomass = sum(Size), BinFrequency = n()) %>% ungroup() %>%
  mutate(NormalizedFrequency = BinFrequency/TotalFrequency*100, NormalizedBiomass = BinBiomass/TotalBiomass*100)

@@

```{r Plot Aggregate size bins}
#Plot Normalized Frequency
#this isn't useful as the normalized Frequency changes with replicate, so it's better to pool all samples together
PlotHistSum<-function(rep.df,cond.df,region.df, y_var, title, species, colorStrain){
ggplot()+
    geom_point(data = rep.df %>% filter(TimePoint=="Day 4")%>% filter(Species == species),
                aes(x=as.factor(LogBin),y=.data[[y_var]], color =.data[[colorStrain]], shape = Region),
               position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75),size=1)+
    geom_point(data = region.df%>% filter(TimePoint=="Day 4")%>% filter(Species == species),
               aes(x=as.factor(LogBin),y=.data[[y_var]], color =.data[[colorStrain]],shape = Region),
               size=3, position = position_dodge(width = .75) )+
    geom_point(data = cond.df%>% filter(TimePoint=="Day 4") %>% filter(Species == species),
               aes(x=as.factor(LogBin),y=.data[[y_var]],  color =.data[[colorStrain]]),size=4, shape = 3,position = position_dodge(width = .75) )+
    #scale_y_log10(breaks = c(100, 10, 1, .1, .01), labels = c(100, 10, 1, .1, .01))+
    facet_grid(.~Species)+
    scale_shape_manual(values=c(16, 1))+
    ggtitle(title)+
    labs(y = paste(y_var,"(%)"),x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
    scale_color_brewer(palette = "Set1")+
    theme_cowplot()+
    panel_border() +
    theme(plot.title = element_text(hjust = 0.5), 
        strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
}
PlotHistSum(HistReplicateSummary,HistConditionSummary,HistCondRegionSum,"NormalizedFrequency", "Normalized Frequency all sizes", "S. aureus")

####---Figure 1C
PlotHistSum(HistReplicateSummary %>% filter(SaStrain %in% c("Sa mono", "co-wt")),
            HistConditionSummary%>% filter(SaStrain %in% c("Sa mono", "co-wt")),
            HistCondRegionSum%>% filter(SaStrain %in% c("Sa mono", "co-wt")),
            "NormalizedFrequency", "Normalized Frequency all sizes", "S. aureus", "Culture")

PlotHistSum(HistReplicateSummary %>% filter(Strain %in% c("wt")),
            HistConditionSummary%>% filter(Strain %in% c("wt")),
            HistCondRegionSum%>% filter(Strain %in% c("wt")),
            "NormalizedFrequency", "Normalized Frequency all sizes", "P. aeruginosa", "Culture")

PlotHistSum(HistReplicateSummary,
            HistConditionSummary,
            HistCondRegionSum,
            "NormalizedFrequency", "Normalized Frequency all sizes", "S. aureus", "SaStrain")

PlotHistSum(HistReplicateSummary%>% filter(Culture =="co"),
            HistConditionSummary%>% filter(Culture =="co"),
            HistCondRegionSum%>% filter(Culture =="co"),
            "NormalizedFrequency", "Normalized Frequency all sizes", "P. aeruginosa", "Strain")

@@

```{r Plot Aggregate vs planktonics}

#Plot Frequency
PlotAggPlank<-function(rep.df,cond.df,region.df, y_var, title, species, colorStrain, facet){
ggplot()+
    geom_point(data = rep.df %>% filter(TimePoint=="Day 4")%>% filter(Species == species),
                aes(x=as.factor(Aggregation),y=.data[[y_var]], color =.data[[colorStrain]], shape = Region),
               position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75),size=1)+
    geom_point(data = region.df%>% filter(TimePoint=="Day 4")%>% filter(Species == species),
               aes(x=as.factor(Aggregation),y=.data[[y_var]], color =.data[[colorStrain]],shape = Region),
               size=3, position = position_dodge(width = .75) )+
    geom_point(data = cond.df%>% filter(TimePoint=="Day 4") %>% filter(Species == species),
               aes(x=as.factor(Aggregation),y=.data[[y_var]],  color =.data[[colorStrain]]),size=4, shape = 3,position = position_dodge(width = .75) )+
    scale_y_log10(breaks = c(100, 10, 1, .1, .01), labels = c(100, 10, 1, .1, .01))+
    facet_grid(.~.data[[facet]])+
    scale_shape_manual(values=c(16, 1))+
    ggtitle(title)+
    labs(y = paste(y_var,"(%)"),x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
    scale_color_brewer(palette = "Set1")+
    theme_cowplot()+
    panel_border() +
    theme(plot.title = element_text(hjust = 0.5), 
        strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
}
###---Figure 1D
PlotAggPlank(plankAggHistRep%>% filter(SaStrain %in% c("Sa mono", "co-wt")),
             plankAggHistCond%>% filter(SaStrain %in% c("Sa mono", "co-wt")),
             plankAggHistCondReg%>% filter(SaStrain %in% c("Sa mono", "co-wt")),
             "AgPlNormBiomass", "Normalized Biomass", "S. aureus", "Culture", "Species")

PlotAggPlank(plankAggHistRep,
             plankAggHistCond,
             plankAggHistCondReg,
             "AgPlNormBiomass", "Normalized Biomass", "S. aureus", "SaStrain","Species")

PlotAggPlank(plankAggHistRep,
             plankAggHistCond,
             plankAggHistCondReg,
             "AgPlNormBiomass", "Normalized Biomass", "P. aeruginosa", "Strain","Culture")

@@

#####
#Plot Data
#####
ggplot()+
  #geom_point(data = sliceDataMeta ,aes(y=NormBiomass,x=Height, color = Condition, group = Replicate),size=.5)+
  geom_smooth(data = sliceDataMeta ,aes(y=NormBiomass,x=Height, color =Condition),size=2)+
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray")+
  theme_cowplot()+
  scale_color_brewer(palette = "Set1")+
  ylim(0,26)+
  facet_grid(Channel~TimePoint)+
  panel_border() +
  coord_flip()
  theme(plot.title = element_text(hjust = 0.5))
#####
#Filter by Max height of the sample
#####  
  #graph the samples height
  ggplot()+
    geom_col(data = sliceDataSumary %>% filter(TimePoint=="Day 4"),aes(x=SampleCode,y=MaxHeight, color = Strain, fill =Culture ),size=2)+
    geom_hline(yintercept = 50)+
    labs(title ="title")+
    scale_color_brewer(palette = "Set2")+
    scale_fill_brewer(palette = "Set1")+
    theme_cowplot()+
    theme(plot.title = element_text(hjust = 0.5))

PlotZsliceSa<-function(){  
  ggplot()+
    geom_smooth(data = sliceDataClean %>% filter(Species == "S. aureus"),aes(y=NormBiomass,x=Height, color = Region),size=2, alpha = .1)+
    #geom_point(data = sliceDataClean%>% filter(Species == species),aes(y=NormBiomass,x=Height, color = Region),size=1, alpha = .5)+
    geom_hline(yintercept = 0, linetype = "dashed", color = "gray")+
    theme_cowplot()+
    scale_color_brewer(palette = "Set1")+
    facet_grid(Strain~.)+
    scale_shape_manual(values = c(1, 3))+
    panel_border() +
    coord_flip()+
    theme(plot.title = element_text(hjust = 0.5))}
PlotZslicePa<-function(){  
  ggplot()+
    geom_smooth(data = sliceDataClean %>% filter(Species == "P. aeruginosa") %>% filter(Culture=="co"),aes(y=NormBiomass,x=Height, color = Region),size=2, alpha = .1)+
    #geom_point(data = sliceDataClean%>% filter(Species == species),aes(y=NormBiomass,x=Height, color = Region),size=1, alpha = .5)+
    geom_hline(yintercept = 0, linetype = "dashed", color = "gray")+
    theme_cowplot()+
    scale_color_brewer(palette = "Set1")+
    facet_grid(Strain~.)+
    scale_shape_manual(values = c(1, 3))+
    panel_border() +
    coord_flip()+
    theme(plot.title = element_text(hjust = 0.5))}
PlotZslicePa()
PlotZsliceSa()

>>>>

PlotBiomasPerSampleAndCondition<-function(df1,df2, df3,xAxis){
ggplot()+ 
    geom_point(data = df1 %>% filter(TimePoint=="Day 4") , aes(x = .data[[xAxis]], y= meanBiomassLog,shape = Region), 
             position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75), size = 4)+
  geom_point(data = df2%>% filter(TimePoint=="Day 4") , aes(x = .data[[xAxis]], y= log10(biomass), shape = Region),size = 1, 
             position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75))+ 
  geom_point(data = df3 %>% filter(TimePoint=="Day 4"), aes(x = .data[[xAxis]], y= meanBiomassLog), shape = 3, size = 4)+
    #scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)), limits = c(1, 100000000))+
      facet_grid(.~Species, scales = "free", space = "free") +
  ggtitle('Total Biomass')+
  labs(x = "",y = bquote(paste("Volume (log10", mu*"m"^3*")")))+
  scale_color_brewer(palette = "Set1")+
  scale_shape_manual(values=c(16, 1))+
  ylim(0,8)+
    theme_cowplot()+
  panel_border() +
  theme(plot.title = element_text(hjust = 0.5), 
        strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
}

PlotMeanAggsPerSampleAndConditionWT<-function(df1,df2, df3){
ggplot()+ 
    geom_point(data = df1 %>% filter(TimePoint=="Day 4"), aes(x = Culture, y= meanAggs,shape = Region), 
             position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75), size = 4)+
  geom_point(data = df2%>% filter(TimePoint=="Day 4"), aes(x = Culture, y= Aggs, shape = Region),size = 1, 
             position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75))+
    geom_point(data = df3 %>% filter(TimePoint=="Day 4"), aes(x = Culture, y= meanAggs),shape = 3,size = 4)+
    scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)), limits = c(10, 100000))+
      facet_grid(.~Species, scales = "free", space = "free") +
  ggtitle('Number of groups of bacteria')+
  labs(x = "",y = "")+
  scale_color_brewer(palette = "Set1")+
  scale_shape_manual(values=c(16, 1))+
  #ylim(0,8)+
    theme_cowplot()+
  panel_border() +
  theme(plot.title = element_text(hjust = 0.5), 
        strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
}

PlotMeanAggsPerSampleAndCondition<-function(df1,df2, df3, xAxis){
ggplot()+ 
    geom_point(data = df1 %>% filter(TimePoint=="Day 4") , aes(x = .data[[xAxis]], y= meanAggs,shape = Region), 
             position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75), size = 4)+
  geom_point(data = df2%>% filter(TimePoint=="Day 4"), aes(x = .data[[xAxis]], y= Aggs, shape = Region),size = 1, 
             position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75))+
    geom_point(data = df3 %>% filter(TimePoint=="Day 4"), aes(x = .data[[xAxis]], y= meanAggs),shape = 3,size = 4)+
    scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)), limits = c(1, 100000))+
      facet_grid(.~Species, scales = "free", space = "free") +
  ggtitle('Number of groups of bacteria')+
  labs(x = "",y = "")+
  scale_color_brewer(palette = "Set1")+
  scale_shape_manual(values=c(16, 1))+
  #ylim(0,8)+
    theme_cowplot()+
  panel_border() +
  theme(plot.title = element_text(hjust = 0.5), 
        strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
}

@@

```
```{r figures 1A,1B and 2A, 2B}
#Biomass wt
PlotBiomasPerSampleAndConditionWT(aggregateListSummaryCondition%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "Pa wt mono"),
                                aggregateListSummaryReplicate %>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "Pa wt mono"), 
                                aggregateListSummaryCondNoRegion%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "Pa wt mono"))
#Biomass Sa and mutants
PlotBiomasPerSampleAndCondition(aggregateListSummaryCondition%>% filter(Culture=="co"),
                                aggregateListSummaryReplicate%>% filter(Culture=="co"),
                                aggregateListSummaryCondNoRegion%>% filter(Culture=="co"),"SaStrain")

@@

#Number of aggregates Sa and mutants
PlotMeanAggsPerSampleAndCondition(aggregateListSummaryCondition%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "Pa wt mono"),
                                aggregateListSummaryReplicate%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "Pa wt mono"), 
                                aggregateListSummaryCondNoRegion%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "Pa wt mono"), "Culture")

PlotMeanAggsPerSampleAndCondition(aggregateListSummaryCondition %>% filter(Culture=="co"),
                                aggregateListSummaryReplicate%>% filter(Culture=="co"), 
                                aggregateListSummaryCondNoRegion%>% filter(Culture=="co"),"SaStrain")
```

@@

#this pipe essentially gets to the product of what fancy histograms do but more efficiently
#First including all sizes

@@

#Summary data frame
HistConditionSummary<-HistCondition %>%
  group_by(Species,SaStrain,Strain,Culture,TimePoint,Condition,LogBin,NormalizedFrequency,NormalizedBiomass) %>% 
  summarize() %>% unique()%>%ungroup() %>%
  group_by(Species,SaStrain,Strain,Culture,TimePoint,Condition) %>% 
  mutate(checkSumFreq =sum(NormalizedFrequency), checkSumBiomass = sum(NormalizedBiomass))
#####
#Now per condition including region. The difference is int the "group_by" part
#####
HistConditionRegin<-aggregateList %>% mutate(LogBin = case_when(Size <= 5 ~ "(.5, 5]",
                        Size<= 10 ~ "(5, 10]",
                        Size<= 100    ~ "(10, 100]",
                        Size<= 1000   ~ "(100, 1000]",
                        Size> 1000  ~ paste0("(1000, ",bquote("\U221E"), ")"))) %>% 
  group_by(Species,Condition,TimePoint,Region)%>% 
  mutate(TotalBiomass = sum(Size), TotalFrequency = n()) %>% ungroup() %>%
  group_by(Species,Condition,TimePoint,Region,LogBin)%>%
  mutate(BinBiomass = sum(Size), BinFrequency = n()) %>% ungroup() %>%
  mutate(NormalizedFrequency = BinFrequency/TotalFrequency*100, NormalizedBiomass = BinBiomass/TotalBiomass*100)

@@

```{r Plot Aggregate size bins}
#Plot Normalized Frequency
#this isn't useful as the normalized Frequency changes with replicate, so it's better to pool all samples together
PlotHistSum<-function(rep.df,cond.df,region.df, y_var, title, colorStrain){
ggplot()+
    geom_point(data = rep.df %>% filter(TimePoint=="Day 4"),
                aes(x=as.factor(LogBin),y=.data[[y_var]], color =.data[[colorStrain]], shape = Region),
               position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75),size=1)+
    geom_point(data = region.df%>% filter(TimePoint=="Day 4"),
               aes(x=as.factor(LogBin),y=.data[[y_var]], color =.data[[colorStrain]],shape = Region),
               size=3, position = position_dodge(width = .75) )+
    geom_point(data = cond.df%>% filter(TimePoint=="Day 4"),
               aes(x=as.factor(LogBin),y=.data[[y_var]],  color =.data[[colorStrain]]),size=4, shape = 3,position = position_dodge(width = .75) )+
    #scale_y_log10(breaks = c(100, 10, 1, .1, .01), labels = c(100, 10, 1, .1, .01))+
    facet_grid(.~Species)+
    scale_shape_manual(values=c(16, 1))+
    ggtitle(title)+
    labs(y = paste("Frequency (%)"),x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
    scale_color_brewer(palette = "Set1")+
    theme_cowplot()+
    panel_border() +
    theme(plot.title = element_text(hjust = 0.5), 
        strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
}
PlotHistSum(HistReplicateSummary,HistConditionSummary,HistCondRegionSum,"NormalizedFrequency", "Normalized Frequency all sizes", "S. aureus")

####---Figure 1C
PlotHistSum(HistReplicateSummary%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "wt mono"),
            HistConditionSummary%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "wt mono"),
            HistCondRegionSum%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "wt mono"),
            "NormalizedFrequency", "Normalized Frequency per size",  "Culture")

PlotHistSum(HistReplicateSummary%>% filter(Culture =="co"),
            HistConditionSummary%>% filter(Culture =="co"),
            HistCondRegionSum%>% filter(Culture =="co"),
            "NormalizedFrequency", "Normalized Frequency per size bin", "Strain")
#To Show the mono for Pa, one way to do it is to include the species in the filtering and do one plot per species. I dont thnink it's reasonable to do it all in one plot

@@

```{r figures 1D and 2D Plot Aggregate vs planktonics}

#Plot Frequency
PlotAggPlankSpecies<-function(rep.df,cond.df,region.df, y_var, title, species, colorStrain, facet){
ggplot()+
    geom_point(data = rep.df %>% filter(TimePoint=="Day 4")%>% filter(Species == species),
                aes(x=as.factor(Aggregation),y=.data[[y_var]], color =.data[[colorStrain]], shape = Region),
               position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75),size=1)+
    geom_point(data = region.df%>% filter(TimePoint=="Day 4")%>% filter(Species == species),
               aes(x=as.factor(Aggregation),y=.data[[y_var]], color =.data[[colorStrain]],shape = Region),
               size=3, position = position_dodge(width = .75) )+
    geom_point(data = cond.df%>% filter(TimePoint=="Day 4") %>% filter(Species == species),
               aes(x=as.factor(Aggregation),y=.data[[y_var]],  color =.data[[colorStrain]]),size=4, shape = 3,position = position_dodge(width = .75) )+
    scale_y_log10(breaks = c(100, 10, 1, .1, .01), labels = c(100, 10, 1, .1, .01))+
    facet_grid(.~.data[[facet]])+
    scale_shape_manual(values=c(16, 1))+
    ggtitle(title)+
    labs(y = paste("Biomass Contribution (%)"),x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
    scale_color_brewer(palette = "Set1")+
    theme_cowplot()+
    panel_border() +
    theme(plot.title = element_text(hjust = 0.5), 
        strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
}
PlotAggPlank<-function(rep.df,cond.df,region.df, y_var, title, colorStrain, facet){
ggplot()+
    geom_point(data = rep.df %>% filter(TimePoint=="Day 4"),
                aes(x=as.factor(Aggregation),y=.data[[y_var]], color =.data[[colorStrain]], shape = Region),
               position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75),size=1)+
    geom_point(data = region.df%>% filter(TimePoint=="Day 4"),
               aes(x=as.factor(Aggregation),y=.data[[y_var]], color =.data[[colorStrain]],shape = Region),
               size=3, position = position_dodge(width = .75) )+
    geom_point(data = cond.df%>% filter(TimePoint=="Day 4"),
               aes(x=as.factor(Aggregation),y=.data[[y_var]],  color =.data[[colorStrain]]),size=4, shape = 3,position = position_dodge(width = .75) )+
    scale_y_log10(breaks = c(100, 10, 1, .1, .01), labels = c(100, 10, 1, .1, .01))+
    facet_grid(.~.data[[facet]])+
    scale_shape_manual(values=c(16, 1))+
    ggtitle(title)+
    labs(y = paste("Biomass contribution (%)"),x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
    scale_color_brewer(palette = "Set1")+
    theme_cowplot()+
    panel_border() +
    theme(plot.title = element_text(hjust = 0.5), 
        strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
}

###---Figure 1D
#this is the current version but the ones below mmight also work if I want to show Pa monos and not facetting the species
PlotAggPlank(plankAggHistRep%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "wt mono"),
             plankAggHistCond%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "wt mono"),
             plankAggHistCondReg%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "wt mono"),
             "AgPlNormBiomass", "Normalized Biomass Contribution", "Culture","Species")

PlotAggPlank(plankAggHistRep%>% filter(Culture == "co"),
             plankAggHistCond%>% filter(Culture == "co"),
             plankAggHistCondReg%>% filter(Culture == "co"),
             "AgPlNormBiomass", "Normalized Biomass Contribution", "Strain","Species")

#these are the other versions
PlotAggPlankSpecies(plankAggHistRep%>% filter(SaStrain %in% c("Sa mono", "co-wt")),
             plankAggHistCond%>% filter(SaStrain %in% c("Sa mono", "co-wt")),
             plankAggHistCondReg%>% filter(SaStrain %in% c("Sa mono", "co-wt")),
             "AgPlNormBiomass", "Normalized Biomass", "S. aureus", "Culture", "Species")

PlotAggPlankSpecies(plankAggHistRep,
             plankAggHistCond,
             plankAggHistCondReg,
             "AgPlNormBiomass", "Normalized Biomass", "S. aureus", "SaStrain","Species")

PlotAggPlankSpecies(plankAggHistRep,
             plankAggHistCond,
             plankAggHistCondReg,
             "AgPlNormBiomass", "Normalized Biomass", "P. aeruginosa", "Strain","Culture")

@@

#####
#Plot Data
#####
ggplot()+
  #geom_point(data = sliceDataMeta ,aes(y=NormBiomass,x=Height, color = Condition, group = Replicate),size=.5)+
  geom_smooth(data = sliceDataMeta ,aes(y=NormBiomass,x=Height, color =Condition),size=2)+
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray")+
  theme_cowplot()+
  scale_color_brewer(palette = "Set1")+
  ylim(0,26)+
  facet_grid(Channel~TimePoint)+
  panel_border() +
  coord_flip()
  theme(plot.title = element_text(hjust = 0.5))
#####
#Filter by Max height of the sample
#####  
  #graph the samples height
  ggplot()+
    geom_col(data = sliceDataSumary %>% filter(TimePoint=="Day 4"),aes(x=SampleCode,y=MaxHeight, color = Strain, fill =Culture ),size=2)+
    geom_hline(yintercept = 50)+
    labs(title ="title")+
    scale_color_brewer(palette = "Set2")+
    scale_fill_brewer(palette = "Set1")+
    theme_cowplot()+
    theme(plot.title = element_text(hjust = 0.5))
#####
PlotZsliceSa<-function(){  
  ggplot()+
    geom_smooth(data = sliceDataClean %>% filter(Species == "S. aureus"),aes(y=NormBiomass,x=Height, color = Region),size=2, alpha = .1)+
    #geom_point(data = sliceDataClean%>% filter(Species == species),aes(y=NormBiomass,x=Height, color = Region),size=1, alpha = .5)+
    geom_hline(yintercept = 0, linetype = "dashed", color = "gray")+
    theme_cowplot()+
    scale_color_brewer(palette = "Set1")+
    facet_grid(Strain~.)+
    scale_shape_manual(values = c(1, 3))+
    panel_border() +
    coord_flip()+
    theme(plot.title = element_text(hjust = 0.5))}
PlotZslicePa<-function(){  
  ggplot()+
    geom_smooth(data = sliceDataClean %>% filter(Species == "P. aeruginosa") %>% filter(Culture=="co"),aes(y=NormBiomass,x=Height, color = Region),size=2, alpha = .1)+
    #geom_point(data = sliceDataClean%>% filter(Species == species),aes(y=NormBiomass,x=Height, color = Region),size=1, alpha = .5)+
    geom_hline(yintercept = 0, linetype = "dashed", color = "gray")+
    theme_cowplot()+
    scale_color_brewer(palette = "Set1")+
    facet_grid(Strain~.)+
    scale_shape_manual(values = c(1, 3))+
    panel_border() +
    coord_flip()+
    theme(plot.title = element_text(hjust = 0.5))}
PlotZslicePa()
PlotZsliceSa()
